Antigenic phenotypes and phylogenetic metrics improve forecasts of seasonal influenza A/H3N2 evolution

### 2019-12-30 manuscript/main.tex
Corrected statement about overfitting of epitope sites
The seven Koel sites did not overfit to historical data.

In the second case, we observed overfitting of sites associated with antigenic drift to historical contexts.
The fitness benefit of mutations that lead to antigenic drift in A/H3N2 is well-documented \cite{Wiley:1981bc,Smith:2004jc,Wolf:2006da,Koel:2013jz}
Although the antigenic importance of seven specific sites in HA has been experimentally validated \cite{Koel:2013jz}, these sites do not explain all antigenic drift observed in natural populations \cite{Neher:2016hy}.
Other attempts to define these so-called ``epitope sites'' have relied on either aggregation of results from antigenic escape assays \cite{Wolf:2006da} or retrospective computational analyses of sites with beneficial mutations \cite{Shih:2007bd,Luksza:2014hj}.
We found that all of these specific definitions suffer from overfitting to the historical context in which they were discovered (Supplemental Table~\ref{sup_table:complete_natural_model_selection}).
These results suggest that the set of sites that contribute to antigenic drift at any given time may depend on both the fitness landscape of currently circulating strains and the immune landscape of the hosts these strains need to infect.
Recent experimental mapping of antigenic escape mutations in A/H3N2 HA with human sera show that the specific sites that confer antigenic escape can vary dramatically between individuals based on their exposure history \cite{Lee2019}.
In contrast to models based on predefined ``epitope sites'', our model based on experimental measurements of antigenic drift did not suffer from overfitting in the validation or test periods.
We suspect that this model was able to minimize overfitting by continuously updating its antigenic model with recent experimental data and assigning antigenic weight to branches of a phylogeny rather than specific positions in HA.

>>>>

In the second case, we observed overfitting of sites associated with antigenic drift to historical contexts.
The fitness benefit of mutations that lead to antigenic drift in A/H3N2 is well-documented \cite{Wiley:1981bc,Smith:2004jc,Wolf:2006da,Koel:2013jz}
Although the antigenic importance of seven specific sites in HA has been experimentally validated \cite{Koel:2013jz}, these sites do not explain all antigenic drift observed in natural populations \cite{Neher:2016hy}.
Other attempts to define these so-called ``epitope sites'' have relied on either aggregation of results from antigenic escape assays \cite{Wolf:2006da} or retrospective computational analyses of sites with beneficial mutations \cite{Shih:2007bd,Luksza:2014hj}.
We found that models based on all of these definitions except for the seven Koel epitope sites overfit to the historical context from which they were identified (Supplemental Table~\ref{sup_table:complete_natural_model_selection}).
These results suggest that the set of sites that contribute to antigenic drift at any given time may depend on both the fitness landscape of currently circulating strains and the immune landscape of the hosts these strains need to infect.
Recent experimental mapping of antigenic escape mutations in A/H3N2 HA with human sera show that the specific sites that confer antigenic escape can vary dramatically between individuals based on their exposure history \cite{Lee2019}.
In contrast to models based on predefined ``epitope sites'', our model based on experimental measurements of antigenic drift did not suffer from overfitting in the validation or test periods.
We suspect that this model was able to minimize overfitting by continuously updating its antigenic model with recent experimental data and assigning antigenic weight to branches of a phylogeny rather than specific positions in HA.
